---
---

<link rel="stylesheet" href="styles.css" type="text/css">


Depending on the underlying pattern of the dose-response curve, there are two
functions to cluster the dose-response patterns. In case we know the pattern
should be monotone (like nuclear area in our DILI dataset), the the function
`monotonePatternClustering` should be used. For cases where no such information
is available (i.e., the pattern could be monotone, umbrella-shaped, etc.), one
may use the function `generalPatternClustering`. 

## Clustering subjects with a general pattern

In order to perform clustering, first of all, we need to transorm our data into
the right format for clustering. As it is already mentioned, this can be done
using `inputDataMaker`. Its output can be used to specify many arguments in
`generalPatternClustering` as we can see in the following command.

Furthermore, one needs to determine the way of treating missing data. The
subjects with missing data can either be ignored (`na.rm = TRUE`, not
recommended), or simply replaced by the mean (`imputationMethod = "mean"`) or
median (`imputationMethod = "median"`) of the observed responses for the
dose-level with missing values.  

The `ORICC` argument determines which of one-stage or two-stage ORICC (or both)
should be used. Argument `transform` makes it possible to perform some usual
transformations on the response  (as the response is already transformed we set
this to `none`). The argument `plotFormat` is is a leftover from `ORIClust`
package which save a figure of the identified patterns. 

`LRT` and `MCT` are determining whether likelihood ratio test (LRT) or multiple
comparisons test (MCT) should be applied or not. The adjustment method for
multiplicity can be specified using the argument `adjustMethod`. LRT is a
permutation test, the number of permutations can be set via  `nPermute`. It is
obvious that when `LRT = FALSE` the value of this argument does not matter. A
seed can be spefied using `useSeed`. 

The argument `theLeastNumberOfMethods` determines the smallest number of methods
which should approve a pattern to be non-flat so that subject can be selected.
Let us give an example, suppose we specify `ORICC = "two"`, also `LRT = TRUE`,
and `MCT = TRUE`. As it is already described, only compounds which are
identified as non-flat by ORICC will be passed to LRT or MCT, so the possible
outcomes of these 3 methods could be (0: not-selected, 1: selected):

```{r, echo = FALSE, eval = FALSE}
toShow0 <- matrix(c(0 , 1, 1, 1, 1, 0, 0, 1, 0 ,1, 0, 0, 0, 1, 1), 5, 3)
toShow <- cbind(toShow0, apply(toShow0, 1, sum))
colnames(toShow) = c("ORICC2", "LRT", "MCT", "Sum")
rownames(toShow) = c("Case1", "Case2", "Case3", "Case4", "Case5")
kableExtra::kable(toShow)
```

Now, `theLeastNumberOfMethods = 3` would accept a non-flat dose-response curve
only if all 3 criteria accepts it, `theLeastNumberOfMethods = 2` would do that
if at least two of them accepts it, and so on. The level of significance for
different tests is specified by `alpha`. In case of very large datasets, one can
use more than one core of their system using `nCores`, the maximum possible
value here is the maximum number of cores.

```{r, eval = FALSE}
generalClust <- generalPatternClustering(inputData = inputData1$inputData, colsData = inputData1$colsData, colID = inputData1$colID, doseLevels = inputData1$doseLevels, numReplications = inputData1$numReplicates, na.rm = FALSE, imputationMethod = "mean", ORICC = "two", transform = "none", plotFormat = "eps", LRT = FALSE, MCT = TRUE, adjustMethod = "BH", nPermute = 1000, useSeed = NULL, theLeastNumberOfMethods = 2, alpha = 0.05, nCores = 1)
```

The outcome of this function is a list providing the `selectedSubjects`, as well
as results of ORICC1 and ORICC2 (if they are requested), included LRT and MCT
results.


## Clustering subjects with a monotone pattern


Imagine we know that our dose-response data should follow a monotone pattern, in
such a case one needs to use the following command for clustering dose-response
patterns:

```{r, eval = FALSE}
monotoneClust <- monotonePatternClustering(inputData = inputData1$inputData, colsData = inputData1$colsData, colID = inputData1$colID, doseLevels = inputData1$doseLevels, numReplications = inputData1$numReplicates, transform = "none", BHorBY = TRUE, SAM = FALSE, testType = c("E2", "Williams", "Marcus", "M", "ModifM"), adjustType = "BH", FDRvalue = c(0.05, 0.05), nPermute= c(1000, 1000), fudgeSAM = "pooled", useSeed = c(NULL, NULL), theLeastNumberOfTests = 5, na.rm = FALSE, imputationMethod = "mean")
```
The first few arguments are the same as in the `generalPatternClustering`. The
argument `BHorBY` asks for performing monotonicity tests specified in `testType`
adjusted for multiplicty using `BH` or `BY` methods. The `adjustType` then
specified the multiplicity adjustment method for monotonicty tests.
`theLeastNumberOfTests` is the same as in `generalPatternClustering`, but now it
applies on the tests specified in `testType`. IF it suits, it is also possible
to perform a SAM procedure (`SAM = TRUE`). 

