---
---

<link rel="stylesheet" href="styles.css" type="text/css">

The initial step to use the `clustDRM` package is to make sure a correctly
formatted dataset is fed to different functions.

For illustration purposes, we simulate dose-response data from a linear model:

```{r}
## Generating a sample for 20 subjects
genData0 <- MCPMod::genDFdata("linear",c(-4, 1), 
		c(0, 5, 10), rep(5, 3), 1)
genData <- data.frame(rep(1, nrow(genData0)), genData0)
colnames(genData)[1] <- "ID"
for (iSim in 2:10){
	genData0 <- MCPMod::genDFdata("linear",c(-4, 1), 
			c(0, 5, 10), rep(5, 3), 1)
	genDatatmp <- data.frame(rep(iSim, nrow(genData0)), genData0)
	colnames(genDatatmp)[1] <- "ID"
	genData <- rbind(genData, genDatatmp)
}
write.csv(genData, "sampleData.csv")

inputDataset <- read.csv("sampleData.csv")
head(inputDataset)
```

While a dataset with such a format is appropriate for modelling purposes, the
clustering functions would need the data in the so-called long-format, where
each row of data contains the responses for all different dose-replications. The
function `inputDataMaker` would make this transform easily possible. One needs
to give the inputDataset, as well as the columns corresponding to dose (in
numeric format), response, and ID. This can be the number of the column, or its
name or a combination of these two. All the three following commands will be
produce the same results.

```{r}
inputData1 <- inputDataMaker(3, 4, 2, inputDataset)
inputData2 <- inputDataMaker("dose", "resp", "ID", inputDataset)
inputData3 <- inputDataMaker(2, "resp", 1, inputDataset)

```

The outcome of the function `inputDataMaker` provides the transformed dataset, 
as well as the unique doses in the study, and number of replications per dose.
The columns correspond to the data (responses) and ID are also provided.
